From Reversible Programs to \\ Univalent Universes and Back

### 2021-10-30 Pi/paper/applications.tex
Formatting

\subsection{Synthesis}

@@

@@

As an example, consider the following problem. Toffoli gate on 3 bits can be extended to 4 bits, inserting a wire in
four possible positions. The function of such gate is then identity on the newly inserted bit, and controlled-controlled
not on the three remaining ones.
\medskip
\extendedToffoli{}
\baselineskip
On the other hand, it is possible to construct a proper 4-bit toffoli gate:
\medskip
\toffoli{}
\baselineskip
Now, the question we want to answer is: is it possible to compose some number of (extended) 3-bit toffoli gates in some way, so as to replicate the
behaviour of a 4-bit toffoli gate?

>>>>

\subsection{Synthesis and verification}

@@

In a similar way we can also verify whether a circuit is correctly implemented: by running the equivalence described
above in the other direction, we can evaluate the circuit to a bijection and compare it extensionally with the intended
one.

@@

As an example, consider the following problem. Toffoli gate on 3 bits can be extended to 4 bits, inserting a wire in
four possible positions. The function of such gate is then identity on the newly inserted bit, and controlled-controlled
not on the three remaining ones.
\medskip
\extendedToffoli{}

\noindent
On the other hand, it is possible to construct a proper 4-bit toffoli gate:
\medskip
\toffoli{}

\noindent
Now, the question we want to answer is: is it possible to compose some number of (extended) 3-bit toffoli gates in some way, so as to replicate the
behaviour of a 4-bit toffoli gate?
